Basic Bibliography and Reference Testing

### 2019-12-03 _support/reference/labelref/labelref_test.tex
references differ hyperlinks by sections

\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, plainpages=false, pdfpagelabels=true, urlcolor=blue]{hyperref}
\usepackage[bottom]{footmisc}

\usepackage{filecontents}
% This creates a bib file called ref.bib in the same folder as the current tex file
\begin{filecontents}{ref.bib}
@article{becker_human_1986,
	title = {Human Capital and the Rise and Fall of Families},
	volume = {4},
	url = {http://ideas.repec.org/a/ucp/jlabec/v4y1986i3ps1-39.html},
	pages = {S1--39},
	number = {3},
	journaltitle = {Journal of Labor Economics},
	author = {Becker, Gary S and Tomes, Nigel},
	urldate = {2012-02-15},
	date = {1986}
}
@article{case_lasting_2005,
	title = {The lasting impact of childhood health and circumstance},
	volume = {24},
	issn = {0167-6296},
	url = {http://www.ncbi.nlm.nih.gov/pubmed/15721050},
	doi = {10.1016/j.jhealeco.2004.09.008},
	pages = {365--389},
	number = {2},
	journaltitle = {Journal of health economics},
	shortjournal = {J Health Econ},
	author = {Case, Anne and Fertig, Angela and Paxson, Christina},
	urldate = {2012-06-13},
	date = {2005-03},
	pmid = {15721050},
	keywords = {Adult, child, Child Welfare, Cohort Studies, Great Britain, Health Status Indicators, Humans, Social Class}
}
@article{conti_understanding_2010,
	title = {Understanding the Early Origins of the Education–Health Gradient},
	volume = {5},
	issn = {1745-6916, 1745-6924},
	url = {http://pps.sagepub.com/content/5/5/585.abstract},
	doi = {10.1177/1745691610383502},
	pages = {585--605},
	number = {5},
	journaltitle = {Perspectives on Psychological Science},
	author = {Conti, Gabriella and Heckman, James J},
	urldate = {2012-02-16},
	date = {2010-09-01},
	keywords = {health, education, genetics, treatment effects}
}
\end{filecontents}

@@

@@

According to \textcite{becker_human_1986}, ipsum dolor sit amet, consectetur adipiscing elit. Integer placerat nunc orci, id pellentesque lacus ullamcorper at. Mauris venenatis gravida magna non dapibus. Nullam vel consequat purus, id luctus dui. Suspendisse vel auctor nulla. Proin ipsum felis, efficitur eu eleifend vitae, efficitur pellentesque mauris \autocite{case_lasting_2005, conti_understanding_2010}.

@@

>>>>

\usepackage{setspace}
\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, plainpages=false, pdfpagelabels=true, urlcolor=blue]{hyperref}
\usepackage[bottom]{footmisc}
\usepackage{blindtext}

\usepackage{filecontents}
% This creates a bib file called ref.bib in the same folder as the current tex file
\begin{filecontents}{ref.bib}
@article{becker_human_1986,
	title = {Human Capital and the Rise and Fall of Families},
	volume = {4},
	url = {http://ideas.repec.org/a/ucp/jlabec/v4y1986i3ps1-39.html},
	pages = {S1--39},
	number = {3},
	journaltitle = {Journal of Labor Economics},
	author = {Becker, Gary S and Tomes, Nigel},
	urldate = {2012-02-15},
	date = {1986}
}
@article{conti_understanding_2010,
	title = {Understanding the Early Origins of the Education–Health Gradient},
	volume = {5},
	issn = {1745-6916, 1745-6924},
	url = {http://pps.sagepub.com/content/5/5/585.abstract},
	doi = {10.1177/1745691610383502},
	pages = {585--605},
	number = {5},
	journaltitle = {Perspectives on Psychological Science},
	author = {Conti, Gabriella and Heckman, James J},
	urldate = {2012-02-16},
	date = {2010-09-01},
	keywords = {health, education, genetics, treatment effects}
}
\end{filecontents}

@@

\maketitle
\begin{abstract}
\singlespacing In this \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{paper}, we look at how to reference sections and reference section page numbers. And we also include in the bibliography links to on which page the references were mentioned. Hyperref is used to show links in subsections in different ways, some clickable, some not.\end{abstract}
\vfill
\pagebreak{}

@@

According to \textcite{becker_human_1986}, ipsum dolor sit amet, consectetur adipiscing elit. Integer placerat nunc orci, id pellentesque lacus ullamcorper at. Mauris venenatis gravida magna non dapibus. Nullam vel consequat purus, id luctus dui. Suspendisse vel auctor nulla. Proin ipsum felis, efficitur eu eleifend vitae, efficitur pellentesque mauris \autocite{becker_human_1986}.

@@

\section{Introduction\label{sec:intro}}
\blindtext\footnote{\autocite{conti_understanding_2010}}.

\section{Data\label{sec:data}}
\Blindtext

\section{Estimation\label{sec:estimate}}
\Blindtext

\section{Conclusion\label{sec:conclude}}

In Section \ref{sec:intro} (Page \pageref{sec:intro}), we introduced the paper. In Section \ref{sec:data} (Page \pageref{sec:data}), we discussed the data. In Section \ref{sec:estimate} (Page \pageref{sec:estimate}), we discussed the estimation results.
\blindtext

\pagebreak
\appendix

\section{References here not Colored or Linked}
\begingroup
{\hypersetup{hidelinks=true}
Now we change settings for the appendix, so that the page numbers do not light up. Earlier they did.

In Section \ref{sec:intro} (Page \pageref{sec:intro}), we introduced the paper. In Section \ref{sec:data} (Page \pageref{sec:data}), we discussed the data. In Section \ref{sec:estimate} (Page \pageref{sec:estimate}), we discussed the estimation results.
}
\endgroup

\section{References here have Red Color}
\begingroup
{\hypersetup{colorlinks=true, linkcolor=red, citecolor=red, plainpages=false, pdfpagelabels=true, urlcolor=red}
	Now we change settings for the appendix, so that the page numbers do not light up. Earlier they did.
	In Section \ref{sec:intro} (Page \pageref{sec:intro}), we introduced the paper. In Section \ref{sec:data} (Page \pageref{sec:data}), we discussed the data. In Section \ref{sec:estimate} (Page \pageref{sec:estimate}), we discussed the estimation results. For more help on the hyperref package's options, see: \href{http://mirror.utexas.edu/ctan/macros/latex/contrib/hyperref/doc/options.pdf}{hyperref package options}.
}
\endgroup
